KidsAIR: manuscript tables/figures

### 2021-06-09 manuscript_tables_figures.Rmd
PM analysis updates. Manuscript revisions from co-author comments.

kids_demographics <- rbind(ak_demographics, nn_demographics, wmt_demographics) %>% 
  filter(!is.na(treatment)) %>% 
  filter(!is.na(child_id_num)) %>% 
  count(area, winter_id, treatment) %>% 
  filter(winter_id != 2)
```

@@

kids_ids <- rbind(ak_ids, nn_ids, wmt_ids) %>% 
  select(-treatment) %>% 
  filter(winter_id == 1) %>% 
  filter(!is.na(home)) %>% 
  mutate(original = 1) %>% 
  right_join(treatments_masked, by = "home") %>% 
  filter(home != "WMA222" & home != "WMA233") %>%
  filter(original == 1)
```

@@

# Count number of households and kids that participated by area and winter
```{r}
# number of households, total and by area
study_homes <- health_exposure_data_sampling_day %>% 
  distinct(home, winter_id, .keep_all = TRUE) %>%
  count(area, winter_id, treatment_assigned)

study_kids <- health_exposure_data_sampling_day %>% 
  select(area, home, child_id_char, child_id_num, winter_id, treatment_assigned) %>% 
  filter(!is.na(child_id_char)) %>% 
  distinct(area, child_id_num, winter_id, .keep_all = TRUE) %>% 
  count(area, winter_id, treatment_assigned)
```

@@

```{r}
# summary data for manuscript tables
char_funct_total <- function(var, data = health_exposure_data_sampling_day){

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  filter(winter_id == 1) %>% 
  #filter(treatment_assigned == "Placebo") %>%
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  mutate(total_n = n()) %>% 
  group_by(area) %>% 
  mutate(area_n = n()) %>% 
  group_by(new_var) %>% 
  mutate(n = n(),
         percent = n()/total_n) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  dplyr::select(new_var, n, percent)
demographics_summary
}

@@

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  filter(winter_id == 1) %>% 
  #filter(treatment_assigned == "Placebo") %>% 
  arrange(new_var) %>% 
  distinct(home, .keep_all = TRUE) %>% 
  mutate(total_n = n()) %>% 
  group_by(treatment_assigned) %>% 
  mutate(area_n = n()) %>% 
  group_by(treatment_assigned, new_var) %>% 
  mutate(n = n(),
         percent = n()/area_n) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  dplyr::select(new_var, n, percent) %>% 
  arrange(treatment_assigned, new_var)
demographics_summary
}

char_funct_total("gender_parent")
char_funct_area("gender_parent")
char_funct_total("gender")
char_funct_area("gender")
char_funct_total("hispanic_parent")
char_funct_area("hispanic_parent")
char_funct_total("race_parent")
char_funct_area("race_parent")
char_funct_total("education_3level")
char_funct_area("education_3level")
char_funct_total("income_3level")
char_funct_area("income_3level")
char_funct_total("home_floors_2level")
char_funct_area("home_floors_2level")
char_funct_total("home_sqft_2level")
char_funct_area("home_sqft_2level")
char_funct_total("home_year_built_2level")
char_funct_area("home_year_built_2level")
char_funct_total("home_pets_2level")
char_funct_area("home_pets_2level")
char_funct_total("home_pets")
char_funct_area("home_pets")
char_funct_total("stove_age_3level")
char_funct_area("stove_age_3level")
char_funct_total("chimney_clean_3level")
char_funct_area("chimney_clean_3level")
char_funct_total("wood_collect_method_2level")
char_funct_area("wood_collect_method_2level")
char_funct_total("wood_collect_2level")
char_funct_area("wood_collect_2level")
char_funct_total("stove_grade_3level")
char_funct_area("stove_grade_3level")
char_funct_total("burn_level_3level")
char_funct_area("burn_level_3level")
char_funct_total("ruca_code")
char_funct_area("ruca_code")
char_funct_total("ruca_code_2")
char_funct_area("ruca_code_2")
char_funct_total("ruca_code_3")
char_funct_area("ruca_code_3")
```

@@

>>>>

kids_demographics <- rbind(ak_demographics, nn_demographics, wmt_demographics) %>% 
  filter(!is.na(treatment)) %>% 
  filter(!is.na(child_id_num)) %>% 
  count(area, winter_id, treatment) %>% 
  filter(winter_id != 2)
kids_demographics
```

@@

kids_ids <- rbind(ak_ids, nn_ids, wmt_ids) %>% 
  select(-treatment) %>% 
  filter(winter_id == 1) %>% 
  filter(!is.na(home)) %>% 
  mutate(original = 1) %>% 
  right_join(treatments_masked, by = "home") %>% 
  filter(home != "WMA222" & home != "WMA233") %>%
  filter(original == 1)

kids_ids
```

@@

# Count number of households and kids that participated by area and winter
```{r}
# number of households, total and by area
study_homes <- health_exposure_data_sampling_day %>% 
  distinct(home, winter_id, .keep_all = TRUE) %>%
  count(winter_id, treatment_assigned)
study_homes

study_kids <- health_exposure_data_sampling_day %>% 
  dplyr::select(area, home, child_id_char, child_id_num, winter_id, treatment_assigned) %>% 
  filter(!is.na(child_id_char)) %>% 
  distinct(area, child_id_char, winter_id, .keep_all = TRUE) %>% 
  count(winter_id, treatment_assigned)
study_kids
```

@@

```{r}
demographics_summary <- health_exposure_data_sampling_day %>% 
  filter(winter_id == 1 | winter_id == 0) %>% 
  arrange(winter_id) %>% 
  #filter(treatment_assigned == "Placebo") %>%
  distinct(child_id_char, .keep_all = TRUE)

# summary data for manuscript tables
char_funct_total <- function(var, data = health_exposure_data_sampling_day){

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  filter(winter_id != 2) %>% 
  #filter(treatment_assigned == "Placebo") %>%
  arrange(area, child_id_char, new_var) %>% 
  distinct(area, child_id_char, .keep_all = TRUE) %>% # change to child_id_char or home as necessary
  mutate(total_n = n()) %>% 
  group_by(area) %>% 
  mutate(area_n = n()) %>% 
  group_by(new_var) %>% 
  mutate(n = n(),
         percent = n()/total_n) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  dplyr::select(new_var, n, percent)
demographics_summary
}

@@

demographics_summary <- data %>% 
  rename(new_var = var) %>% 
  filter(winter_id != 2) %>% 
  #filter(treatment_assigned == "Placebo") %>% 
  arrange(area, child_id_char, new_var) %>% 
  distinct(area, child_id_char, .keep_all = TRUE) %>% # change to child_id_char or home as necessary
  mutate(total_n = n()) %>% 
  group_by(treatment_assigned) %>% 
  mutate(area_n = n()) %>% 
  group_by(treatment_assigned, new_var) %>% 
  mutate(n = n(),
         percent = n()/area_n) %>% 
  distinct(new_var, .keep_all = TRUE) %>% 
  dplyr::select(new_var, n, percent) %>% 
  arrange(treatment_assigned, new_var)
demographics_summary
}

# distinct by child - change var in functions above to child_id_char
char_funct_total("gender")
char_funct_area("gender")
char_funct_total("hispanic_parent")
char_funct_area("hispanic_parent")
char_funct_total("race_child")
char_funct_area("race_child")

# distinct by home - change var in functions above to home
char_funct_total("gender_parent")
char_funct_area("gender_parent")
char_funct_total("hispanic_parent")
char_funct_area("hispanic_parent")
char_funct_total("race_parent")
char_funct_area("race_parent")
char_funct_total("education_3level")
char_funct_area("education_3level")
char_funct_total("income_3level")
char_funct_area("income_3level")
char_funct_total("home_floors_2level")
char_funct_area("home_floors_2level")
char_funct_total("home_sqft_2level")
char_funct_area("home_sqft_2level")
char_funct_total("home_year_built_2level")
char_funct_area("home_year_built_2level")
char_funct_total("home_pets_2level")
char_funct_area("home_pets_2level")
char_funct_total("home_pets")
char_funct_area("home_pets")
char_funct_total("stove_age_3level")
char_funct_area("stove_age_3level")
char_funct_total("chimney_clean_3level")
char_funct_area("chimney_clean_3level")
char_funct_total("wood_collect_method_2level")
char_funct_area("wood_collect_method_2level")
char_funct_total("wood_collect_2level")
char_funct_area("wood_collect_2level")
char_funct_total("stove_grade_3level")
char_funct_area("stove_grade_3level")
char_funct_total("burn_level_3level")
char_funct_area("burn_level_3level")
char_funct_total("ruca_code")
char_funct_area("ruca_code")
char_funct_total("ruca_code_2")
char_funct_area("ruca_code_2")
char_funct_total("ruca_code_3")
char_funct_area("ruca_code_3")
```

@@

# Check ambient temp within groups of self-reported relative stove use
```{r}
analysis_data <- read_rds(paste0(file_path, 
                                 "Output/kids_analysis_data_2obs_per_child.rds"))

summary_results <- analysis_data %>% 
  select(home, area, winter_id, burn_level_3level, amb_temp_lrti) %>% 
  group_by(burn_level_3level) %>% 
  summarize(mean(amb_temp_lrti, na.rm = T),
            median(amb_temp_lrti, na.rm = T))

summary_results
```
